---
title: "German Credit Data Set Analysis"
author: "Utku Erdogan"
date: "May 8, 2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r include=FALSE}
```

####INDEX

#####1.Introduction
#####1.1 Purpose of Project
#####2.Data
#####2.1.Structure of Data
#####2.2.Data Visualization
#####2.3.Data Manipulation
#####2.4.Data Analysis
#####3.Model
#####3.1.Insert Population
#####3.2.Implementation Modelling
#####3.3.Result of Modelling
#####4.Result
#####5.Resource



####1.Introduction

#####1.1 Purpose of Project

German Credit dataset will be implemented logistic regression modelling which predict a target as "Good" and "Bad" on Kaggle website. Explanatory variables will be used in modelling. Methodology will be used Stepwise.

####2.Data

#####2.1.Structure of Data
Structure of Data is analyzed via related function in R. It shows first 5 rows on below side. 


```{r}
library(knitr)
kable(head(german_credit_data <- read.csv(file="C:/Users/U085461/Documents/R/Project/german_credit_data.csv")))
```

Changing name of first column

```{r}
names(german_credit_data)[1]<-"ID"
```

It shows structure of data

```{r}
class(german_credit_data)
dim(german_credit_data)
str(german_credit_data)
summary(german_credit_data)
```


It shows null rows on data

```{r}

library(mice)
library(lattice)

md.pattern(german_credit_data)
```

522 rows is not null

#####2.2.Data Visualization


Numeric variables show distribution. The histograms show on below side

```{r}
german_credit_data_age<-hist(german_credit_data$Age,
                             main="Histogram for Age", 
                             xlab="Age", 
                             border="blue", 
                             col="green",
                             prob = TRUE)
lines(density(german_credit_data$Age))

german_credit_data_credit.amount<-hist(german_credit_data$Credit.amount,
                                       main="Histogram for Credit.amount", 
                                       xlab="Credit.amount", 
                                       border="blue", 
                                       col="green",
                                       prob = TRUE)
lines(density(german_credit_data$Credit.amount)) 

german_credit_data_duration<-hist(german_credit_data$Duration,
                                  main="Histogram for Duration", 
                                  xlab="Duration", 
                                  border="blue", 
                                  col="green",
                                  prob = TRUE)
lines(density(german_credit_data$Duration))

```

Categorical variables show with bar chart on below side

```{r}
barchart(table(german_credit_data$Sex), 
         main="Sex Distribution", 
         xlab="Number of Sex")

barchart(table(german_credit_data$Housing), 
         main="Housing Distribution", 
         xlab="Number of Housing")

barchart(table(german_credit_data$Saving.accounts), 
         main="Saving.accounts Distribution", 
         xlab="Number of Saving.accounts")

barchart(table(german_credit_data$Purpose), 
         main="Purpose Distribution", 
         xlab="Number of Purpose")

barchart(table(german_credit_data$Risk), 
         main="Risk Distribution", 
         xlab="Number of Risk")

barchart(table(german_credit_data$Checking.account), 
         main="Checking.account Distribution", 
         xlab="Number of Checking.account")
```
```{r}
```


#####2.3.Data Manipulation

Null rows exclude on dataset. First 5 rows show on below side 


``` {r}
library(dplyr)

kable(head(df <- filter(german_credit_data,is.na(Checking.account))))

kable(head(german_credit_data_v1 <- anti_join(german_credit_data,df,by="ID")))

kable(head(df_1 <- filter(german_credit_data,is.na(Saving.accounts))))

kable(head(german_credit_data_v2 <- anti_join(german_credit_data_v1,df_1,by="ID")))

str(german_credit_data_v2)
library(plyr)
german_credit_data_v2$Risk<- revalue(german_credit_data_v2$Risk, c("bad"="1"))
german_credit_data_v2$Risk<- revalue(german_credit_data_v2$Risk, c("good"="0"))
```


German_credit_data_v2 is last updated of data 

#####2.4.Data Analysis
######2.4.1.Correlation Analysis

All numeric variables is done correlation analysis. When correlation value is greater than 0.75, this variable is excluded.  
``` {r}
library(corrplot)
library(RColorBrewer)

#correlation
x <- cor(german_credit_data_v2[,unlist(lapply(german_credit_data_v2, is.numeric))])
x
#correlation visualization
corrplot(x, type="upper", order="hclust",
         col=brewer.pal(n=8, name="RdYlBu"))

corrplot(x,type="lower")

```


####3.MODEL

#####3.1.Insert Population

Dataset will be divided  purpose which of train dataset is %70 and test dataset is %30    


```{r}
require(caTools) 
set.seed(123) 
sample = sample.split(german_credit_data_v2,SplitRatio = 0.70)
train =subset(german_credit_data_v2,sample ==TRUE)
test=subset(german_credit_data_v2, sample==FALSE)
```

#####3.2.Implementation Modelling

It is set logistic regression modelling on cleaning dataset. Results show on below side.

```{r}
full<-glm(Risk~., family=binomial, data=train)
summary(full)
```

When Vif values is greater than 2.5, this variable is excluded.  

``` {r}
#vif values
car::vif(full)
#ok
```

All Vif of values is lower than 2.5, so all variable is not excluded 

If Pr(>|z|) values is above %0.05, this varible will be explanatory and selected  

Selected variables;
-Saving.accounts
-Duration
-Checking.account
-Purpose

It will be set modelling again on these variables 

```{r}
full1<-glm(Risk~Saving.accounts+Duration+Checking.account+Purpose, family=binomial, data=train)
summary(full1)
```

```{r}
full2<-glm(Risk~Saving.accounts+Duration+Checking.account+Purpose+Sex, family=binomial, data=train)
summary(full2)
```

Alternative Modelling 1

```{r}
library(ROCR)

p <- predict(full1, newdata=test, type="response")
fitted.results <- predict(full1,newdata=test,type='response')
fitted.results <- ifelse(fitted.results > 0.5,1,0)

misClasificError <- mean(fitted.results != test$Risk)
print(paste('Accuracy',1-misClasificError))

```

Alternative Modelling 2

```{r}
library(ROCR)

p <- predict(full2, newdata=test, type="response")
fitted.results <- predict(full2,newdata=test,type='response')
fitted.results <- ifelse(fitted.results > 0.5,1,0)

misClasificError <- mean(fitted.results != test$Risk)
print(paste('Accuracy',1-misClasificError))

```

#####3.3.Result of Modelling
    Result of modelling is analyzed which accuracy is under %50.  For using modelling accuracy must be above %50. 
    When gender is added as variable on modelling, explanatory of modelling increases. In spite of incrasing explanatory of modelling, Alternative Model 1 is selected which is less variable 
    

    
#####4.Result
    First of all, German Credit Dataset is analyzed via R function from Kaggle website. Data is distributation analysis.After data visualization is done.
    Secondly null rows is excluded from data. The data is divided as a train and test. Train dataset is modelling and train dataset is modelling for test.
    Finally, Alternative Model 1 is selected. Accuracy is %38 so, Model is redevelopment another variable. Using variables were not explanatory not enough.  

#####5.Resource
https://www.kaggle.com/uciml/german-credit



    
